A Context Menu for the Real World: Controlling Physical Appliances Through Head-Worn Infrared Targeting

### 2013-09-18 doc/sigchi14/device.tex
refinments
typos, adding a example

\section{Hardware Device}
\begin{figure}[t]
\centering
\includegraphics[width=1.0\columnwidth]{figures/glass-with-ir}
\caption{Our augmented Glass prototype has a frame-mounted infrared emitter.}
\label{fig:glass}
\end{figure}
\begin{figure}[t]
\centering
\includegraphics[width=1.0\columnwidth]{figures/architecture}
\caption{In our system architecture, selection is initiated through infrared but confirmed over 802.15.4. This permits wearers to move their head freely after connecting to an appliance. In the research prototype, users have to carry an additional microcontroller board that marshalls messages between Glass' Bluetooth radio an IR/802.15.4, but our custom hardware could also be integrated into the wearable device.}
\label{fig:architecture}
\end{figure}

@@

\afterpage{
\begin{figure}[t!]
\centering
\includegraphics[width=1.0\columnwidth]{figures/glass-ir-coverage}
\caption{Different IR configurations suggest that usable beam widths of 2 to 4 feet and distances up to 16 feet }
\label{fig:coverage}
\end{figure}

>>>>

\section{Hardware Device}
\begin{figure}[t]
\centering
\includegraphics[width=1.0\columnwidth]{figures/glass-with-ir}
\caption{Our augmented Glass prototype has a frame-mounted infrared emitter.}
\label{fig:glass}
\end{figure}
\begin{figure}[t]
\centering
\includegraphics[width=1.0\columnwidth]{figures/architecture}
\caption{In our system architecture, selection is initiated through infrared but confirmed over 802.15.4. This permits wearers to move their head freely after connecting to an appliance. In the research prototype, users have to carry an additional microcontroller board that marshals messages between Glass' Bluetooth radio an IR/802.15.4, but our custom hardware could also be integrated into the wearable device.}
\label{fig:architecture}
\end{figure}

@@

\afterpage{
\begin{figure}[t!]
\centering
\includegraphics[width=1.0\columnwidth]{figures/glass-ir-coverage}
\caption{Different IR configurations suggest usable beam widths of 2 to 4 feet and distances up to 16 feet }
\label{fig:coverage}
\end{figure}

### 2013-09-18 doc/sigchi14/interaction.tex
typos, adding a example

{\bf Control:} Glass displays a user interface for parameters of the chosen appliance. Upon connection, the current status of the appliance is retreived by Glass and shown on the UI. The interface is controlled with the temple-mounted touchpad through the following gesture set: tapping toggles discrete parameters (such as power for a lamp as Figure~\ref{fig:ui_controls}(A)); single finger swipe changes between available parameters; double finger swipe adjusts continuous parameters (such as volume for a video player as Figure~\ref{fig:ui_controls}(B)). This scheme was chosen because the touchpad is only comfortably operable in the coronal plane (front to back) but not in the saggital plane (up and down). 
Control commands are sent over XBee radios.

>>>>

{\bf Control:} Glass displays a user interface for parameters of the chosen appliance. Upon connection, the current status of the appliance is retreived by Glass and shown on the UI. The interface is controlled with the temple-mounted touchpad through the following gesture set: tapping toggles discrete parameters (such as power for a lamp as Figure~\ref{fig:ui_controls}(A)); single finger swipe changes between available parameters; double finger swipe adjusts continuous parameters (such as volume for a video player as Figure~\ref{fig:ui_controls}(B)). This scheme was chosen because the touchpad is only comfortably operable in the coronal plane (front to back) but not in the sagittal plane (up and down). 
Control commands are sent over XBee radios.
